%***************************************************************************
%
%  Copyright (c) 2003-2020 Clifford Thompson
%
%  This program is free software: you can redistribute it and/or modify
%  it under the terms of the GNU General Public License as published by
%  the Free Software Foundation, either version 3 of the License, or
% (at your option) any later version.
%
%  This program is distributed in the hope that it will be useful,
%  but WITHOUT ANY WARRANTY; without even the implied warranty of
%  MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
%  GNU General Public License for more details.
%
%  You should have received a copy of the GNU General Public License
%  along with this program.  If not, see <http://www.gnu.org/licenses/>.
%
%**************************************************************************

\resumesection{Relevant Employment History}

\resumejob
{Software Engineer IV / Team Lead / Git Trainer}
{MacDonald Dettwiler \& Associates, Richmond, B.C.}
{July 2016 - Present}

\vspace{0.1 cm}
\resumeindent{1cm}\resumeobjective{I am presently working as a Technical Authority on the Automated Charting and Encoding (ACE) project. The ACE is a web application that is used by the National Geospatial-Intelligence Agency (NGA), and the Royal Australian Air Force to generate and modify Terminal and Enroute Charts. The web application is implemented under Windows using various technologies including Perl, Javascript, AngularJS, HTML, SQL, Selenium, and Git.}

\vspace{0.4 cm}
\resumeindent{1cm}\resumeobjective{From Jan 2017 to Aug 2018, I worked on the Global Procedure Designer (GPD) project, and was responsible for leading a team of 2 developers. GPD is a software product that is used by the United States Air Force (USAF) to automate the design of airplane landing/departure procedures for airports throughout the world. GPD is implemented under Windows using various technologies including as C++, XML, PostgreSQL, Visual Studio, and Subversion for version control.}

\vspace{0.4 cm}
\resumeindent{1cm}\resumeobjective{From July 2016 to Jan 2017, worked on the Performance Data Management System (PDMS) project. PDMS is a microservices solution for Dragonfly Aeronautics LLC, that allow clients to query the maximum amount that
an aircraft can accommodate, and still avoid obstacles/terrain for a given departure procedure. The system was implement under Linux using various technologies including C++, Python \& Flask, Fortran, CMake, Emacs, and Git for version control.}

\newpage

\resumesection{Relevant Employment History}
\resumejob
{Web Development Consultant}
{Beantstalk Behaviour Consulting, New Westminster, B.C.}
{November 2011 - Present}

\vspace{0.1 cm}
\resumeindent{1cm}\resumeobjective{Construction and maintenance of Beanstalk Behaviour Consulting's web presence. Various technologies are being used, including Wordpress.}
%{This instructor position entailed the following responsibilities:}
        %\rb{Successful construction and launch of Beanstalk Behaviour Consulting's \href{http://beanstalkbehaviour.com}{web presence}.}
        %\rb{On going maintence of web presence and content management.}

\resumejob
{Software Engineer \& Product Owner}
{NetApp Canada, Vancouver, B.C.}
{March 2011 - July 2016}

\vspace{0.1 cm}
\resumeindent{1cm}\resumeobjective{NetApp is a Fortune 500 company that builds Enterprise-scale data storage.
I was a member of a dynamic Agile team that is working on next generation scale-out containers for Big Data and Cloud Storage needs. The solutions have been incorporated into the 8.1, 8.2, and 8.3 releases of the DataONTAP Operating System. From November 2014 to January 2016, I acted as the Product Owner for the CLI interface. The system was implement under Linux \& FreeBSD using various technologies including C++, Emacs, and Git \& Perforce for version control.}
%{This software engineering position entails the following responsibilities:}
%\rb{Collaborative development within a distributed team on Cloud and Big Data solutions}
%\rb{Authorship of Design and Functional Specifications}
%\rb{Acted as CLI Product Owner from November 2014 to January 2016}
%\rb{Driving continual improvement of Agile and development practices.}
%\rb{Creation and Facilitation of "Hackathons" for Vancouver colleagues}

\resumejob
{Software Engineer \& Team Lead}%(SDP, IPDS, \& NCOT Projects)}
{MacDonald Dettwiler \& Associates, Richmond, B.C.}
{October 2004 - March 2011}

\vspace{0.1 cm}
\resumeindent{1cm}\resumeobjective{From 2009-2011, I worked on the "One Engine Inoperative" extension to the Global Procedure Designer software. OEI-GPD is a software product that allow clients to query the maximum amount that an aircraft can accommodate, and still avoid obstacles/terrain for a given departure procedure. The client for the software is the United States Air Force, and the system is implemented under a Windows platform using C++, and Subversion for version control.}

\vspace{0.4 cm}
\resumeindent{1cm}\resumeobjective{From 2007-2009, I worked on the IPDS project. IPDS is a software product that will be used by the Federal Aviation Administration to automate the design of airplane landing procedures for airports throughout North America. I was responsible for leading a team of 3-6 developers through 800 person days of work. Previous to that, I was responsible for the development of the web services component which allows the IPDS application to interact with the FAA's remote aviation databases. IPDS is implemented using various technologies such as C++, ANSI C, XML, and XSLT, under a Windows platform, and Subversion for version control.}

\vspace{0.4 cm}
\resumeindent{1cm}\resumeobjective{From 2004-2007, worked on combat simulators for the Canadian Navy (NCOT). NCOT is a combat simulator for the operations room equipment of the various Canadian Naval ships. The system is realized as a multi-processed and networked simulation which can span up to 50 machines. In particular, I was involved with the simulation of the Submarine Fire Control System. I also lead the porting and regression testing of the Submarine Fire Control System from UNIX to Linux. NCOT was implemented using various technologies such as ANSI C89, Motif, Xwindows, and Emacs, under HP UNIX and Linux Platforms, and Razor for version control.}
%{This software engineering position entailed the following responsibilities:}
%        \rb{Complete software life-cycle experience using stringent engineering processes}
%        \rb{Implementing large-scale software(1.5M+ SLOC) in complex, and distributed environments}
%       \rb{Delivering software products to high profile clients (USAF, FAA, \& Canadian Navy)}
%        \rb{Leading and mentoring colleagues, increasing team effectiveness}
%       \rb{Successfully leading/mentoring/tracking a team through a large project plan (800 person-days).}

%\blfootnote{\hspace{-0.55cm}Detailed CV and references available upon request.}
%\resumejob
%{Software Engineer - Instrument Procedure Design System (IPDS)}
%{MacDonald Dettwiler \& Associates, Richmond, B.C.}
%{October 2007 - Present}
%{This software engineering position entailed the following responsibilities:}

%         \rb{Designed and developed high quality web service components for the FAA}
%	\rb{Reduced development costs by adapting various leading-edge technologies}
%	\rb{Increased company visibility by contributing to the Apache Axis2 open-source project}

%\resumejob
%{Software Engineer - Naval Combat Operator Trainers (NCOT)}
%{MacDonald Dettwiler \& Associates, Richmond, B.C.}
%{October 2004 - October 2007}
%{This software engineering position entailed the following responsibilities:}

%	\rb{Created high quality software designs using stringent development practices}
%	\rb{Implemented software in a complex multi-process and distributed environment}
%	\rb{Delivered software products that exceeded the Canadian Navy's expectations}
%	\rb{Assisted in leading and mentoring colleagues, increasing team effectiveness}
        %\rb{Handled sensitive Canadian information in a professional and conscientious manner}
%	\rb{Increased team knowledge-base by chairing technical meetings and presentations}



\resumejob
{Software Engineer \& Project Engineer (Self-Employed)}
{TAD Radio of Canada Incorporated, Prince George, B.C.}
{September 2003 - August 2004}

\vspace{0.1 cm}
\resumeindent{1cm}\resumeobjective{This was an independent contract for Software Engineering to TAD Radio
of Canada. The M-Series Programmer allows TAD technicians/dealers to program various models from TAD's M-Series line of VHF-band radios on all Windows-based machines (Win9x - WinXP). Rigorous software development methodology was used throughout the project including the requirements elicitation \& definition, software design, implementation, quality testing, and deployment. Borland C++ Builder used for implementation, CVS for version control. Various serial/parallel communications protocols were designed \& implemented.}

%{This lead developer position entailed the following responsibilities:}
        %\rb{Elicited TAD for software/user needs resulting in a well-defined requirements document}
        %\rb{Rigorous software methodology was used to obtain a high quality software design}
        %\rb{Final software product exceeded TAD's expectations for usability and quality}
        %\rb{Elicitation of software \& user requirements, creating requirements document}
        %\rb{System design, implementation (including code re-use), documentation, \& deployment}
        %\rb{Full details of this project can be found in the \hyperlink{research}{Selected Research and Projects} section}

%\blfootnote{$^{\dagger}$ References are available upon request.}

\newpage
\resumesection{Relevant Employment History}

\resumejob
{Laboratory Instructor - C++ \& Digital Computer Architecture}
{University of Northern British Columbia, Prince George, B.C.}
{May 1998 - May 2003}

\vspace{0.1 cm}
\resumeindent{1cm}\resumeobjective{I was responsible for running the lab section of the Digital Computer Architecture course at UNBC. I generated/administered student quizzes \& assignments and increased student knowledge through creative lectures and individual support. I was also involved in creating technical documentation for lab equipment to improve usability for the students.}
%{This instructing position entailed the following responsibilities:}
        %\rb{Increased student knowledge through creative lectures and individual support}
        %\rb{Generated/administered student quizzes \& assignments}
        %\rb{Created technical documentation for lab equipment to improve usability}
        %\rb{Provided additional assistance to students outside of the lab sessions}

\resumejob
{Summer Computer Camp Instructor - Java Programming}
{University of Northern British Columbia, Prince George, B.C.}
{May 2002 - August 2002}
{This instructor position entailed the following responsibilities:}

        \rb{Created radio, web, \& poster advertisements that increased camp exposure}
        \rb{Recruited potential UNBC students through high school summer camps}
        \rb{Motivated student enthusiasm using dynamic mini-projects}
%	\rb{Generating lecture notes, lecturing to highschool students}
%	\rb{General advertisement throughout the city, development of camp webpage}

%\resumejob
%{Laboratory Assistant - Introductory C++ Programming}
%{University of Northern British Columbia}
%{September 2000 - December 2000}
%{This position, supervised by Dr. Waqar Haque, entailed the following responsibilities:}

%	\rb{Assisting students with their programming assignments}
%	\rb{Generating/marking/administering student quizzes/assignments}

%\resumesection{Other Employment History}

\resumejob
{Photolab Technician}
{Real Canadian Superstore, Prince George, B.C.}
{August 1996 - June 1999}
{This customer service position entailed the following responsibilities:}
\rb{Negative processing/photo-finishing, equipment maintenance}
\rb{Handling and storage of dangerous chemicals}
\rb{Customer assistance}
%	\rb{Highly skilled negative processing, color correction \& photo finishing}
%	\rb{Maintained chemical balances to ensure correct colour quality standards}
%	\rb{Provided customer service and answered customer inquiries}
%
%	\rb{Offered resolutions to dissatisfied customers for win-win outcome}

%\resumejob
%{Mill Worker}
%{Dollar Saver Lumber Ltd.}
%{October 1994 - June 1999}
%{This position entailed the following responsibilities:}

%	\rb{Operating forklift \& edger, manual labour, painting, landscaping}


%\resumesection{Volunteer History}

%\resumejob
%{Volunteer Radio DJ - CFUR 88.7 FM}
%{University of Northern British Columbia}
%{January 2001 - December 2002}
%{This volunteer position entailed the following responsibilities:}

%   \rb {Creation of programming content for "Pink Pank Punk" program}
%   \rb {Operation of broadcasting equipment, advertising of CFUR in the community}
%   \rb {Adherence to CRTC regulations}


%\resumejob
%{Volunteer Fire Fighter}
%{Pineview Volunteer Fire Department, Prince George, B.C.}
%{October 1995 - May 1999}
%{This team-oriented volunteer position entailed the following responsibilities:}

%	\rb{Increased community safety using fire suppression and emergency first aid}
%	\rb{Competed in auto extrication competitions resulting in community pride}
%	\rb{Fire suppression \& investigation, auto extrication, emergency first aid}


\blfootnote{\hspace{-0.55cm}Complete work history and references available upon request.}
%\blfootnote{$^{\dagger}$CV and references are available upon request.}
